Application of Machine Learning to Predict the Optoelectronic Properties of Benzobisazoles

### 2014-06-27 paper/paper.tex
Add updates to the paper

\begin{abstract}
Because there are always more molecules to test than time, there is a need to quickly be able to rule out structures that are unsuitable for further research. The method presented here takes advantage of common structural features of molecules to decrease the required computational expense that can be seen equivalent Density Functional Theory calculations. By using machine learning methods, the HOMO, LUMO, and band gap can be predicted to within 0.09 eV, 0.08 eV, and 0.10 eV respectively for benzobisazoles. These results also come with the added benefit of being 30,000,000 times faster than the equivalent DFT calculation.
\end{abstract}

@@

\section{Naming Scheme}

@@

@@

@@

 \begin{figure}[H]
   \begin{center}
     \includegraphics[width=5.5in]{figures/allbars2.pdf}
   \end{center}
   \caption{Results}
   \label{fig:results}
 \end{figure}

@@

Overall, the support vector machines with Gaussian kernel had the best performance across all of the goal features and all of the feature vectors. This matches similarly too the results seen by \hl{.... [CITE]}; however, they found that the laplacian kernel performed the best. The suspected reason for the difference in the two results is thought to be because their method involved single atoms as features, whereas this method was dealing with entire functional groups. The smoothness of the gaussian distribution is probably a better estimator in that (especially with something like a phenyl ring). The optimized parameters for the method were found to be $C \approx 10$ and $\gamma \approx 0.05$.

@@

\begin{table}[H]
  \centering
  \caption{LUMO Results}
  \begin{tabular}{llr}
            Feature Vector     & Method       & MAE (eV)                \\
    \hline\hline
    \multirow{7}{*}{Naive}     & Mean Value   & 0.4475 $\pm$ 0.037 \\
                               & Linear       & 0.1900 $\pm$ 0.028 \\
                               & Linear Ridge & 0.1862 $\pm$ 0.025 \\
                               & Tree         & 0.1529 $\pm$ 0.007 \\
                               & k-NN         & 0.2351 $\pm$ 0.019 \\
                               & SVM Gauss    & \textbf{0.1055 $\pm$ 0.010} \\
                               & SVM Laplace  & 0.1454 $\pm$ 0.014 \\
    \hline
    \multirow{7}{*}{Decay}     & Mean Value   & 0.4475 $\pm$ 0.037 \\
                               & Linear       & 0.1816 $\pm$ 0.026 \\
                               & Linear Ridge & 0.1801 $\pm$ 0.026 \\
                               & Tree         & 0.1510 $\pm$ 0.024 \\
                               & k-NN         & 0.2323 $\pm$ 0.017 \\
                               & SVM Gauss    & \textbf{0.1022 $\pm$ 0.015} \\
                               & SVM Laplace  & 0.1317 $\pm$ 0.012 \\
    \hline
    \multirow{7}{*}{Decay with Length Corrections} & Mean Value   & 0.4475 $\pm$ 0.037 \\
                               & Linear       & 0.1847 $\pm$ 0.027 \\
                               & Linear Ridge & 0.1828 $\pm$ 0.027 \\
                               & Tree         & 0.1540 $\pm$ 0.023 \\
                               & k-NN         & 0.2348 $\pm$ 0.014 \\
                               & SVM Gauss    & \textbf{0.1029 $\pm$ 0.012} \\
                               & SVM Laplace  & 0.1331 $\pm$ 0.012 \\
    \hline
    \multirow{7}{*}{Decay with Predictions} & Mean Value   & 0.4475 $\pm$ 0.037 \\
                               & Linear       & 0.1233 $\pm$ 0.012 \\
                               & Linear Ridge & 0.0877 $\pm$ 0.011 \\
                               & Tree         & 0.0863 $\pm$ 0.010 \\
                               & k-NN         & 0.1699 $\pm$ 0.017 \\
                               & SVM Gauss    & \textbf{0.0792 $\pm$ 0.009} \\
                               & SVM Laplace  & 0.0922 $\pm$ 0.009 \\
    \hline\hline
  \end{tabular}
  \label{tab:gapresults}
\end{table}

>>>>

\begin{abstract}
Because there are always more molecules to test than time, there is a need to quickly be able to rule out structures that are unsuitable for further research. The method presented here takes advantage of common structural features of molecules to decrease the required computational expense that can be seen equivalent Density Functional Theory calculations. By using machine learning methods, the HOMO, LUMO, and band gap can be predicted to within 0.09 eV, 0.08 eV, and 0.10 eV respectively for the benzobisazole structures tested. These results also come with the added benefit of being 30,000,000 times faster than the equivalent DFT calculation.
\end{abstract}

@@

\section{Systems of Interest}

For this study, we will be looking at the optoelectronic properties of benzobisazoles, a class of molecules comprised of a three fused ring core. This core is crucial in the fact that it it is highly conjugated which allows for better electron transfer and consequently make them better as organic solar cells. In addition to the core of the benzobisazole there are four different directions from the core that can be extended with various rings and other conjugated systems to attempt to tune the properties of the molecule.

To aid in electron transfer, these structures were picked such that they were highly planer \hl{(angle function?)}

\subsection{Naming Scheme}

@@

\begin{figure}[H]
  \begin{center}
    \includegraphics[width=4.5in]{figures/features.pdf}
  \end{center}
  \caption{Visual Representations of the respective Feature Vector types. \textbf{1.} Naive. \textbf{2.} Decay. \textbf{3.} Decay with length corrections.}
  \label{fig:features}
\end{figure}

@@

\hl{????}
\subsection{Mean Value}
\subsection{Linear Regression}
\subsection{Linear Ridge Regression}
\subsection{Tree Regression}
\subsection{k-Nearest Neighbors}
\subsection{Support Vector Machines}
\subsubsection{Gaussian Kernel}
\subsubsection{Laplacian Kernel}
\hl{????}

@@

 \begin{figure}[H]
   \begin{center}
     \includegraphics[width=5.5in]{figures/allbars2.pdf}
   \end{center}
   \caption{Results. The far left column of each of the graphs can be seen as a baseline value for the set. So from there, any values that are lower than that value are better (with the optimal value being 0.0 eV). For the numerical values, refer to the Appendix.}
   \label{fig:results}
 \end{figure}

@@

Overall, the support vector machines with Gaussian kernel had the best performance across all of the goal features and all of the feature vectors. This matches similarly to the results seen by \hl{.... [CITE]}; however, they found that the laplacian kernel performed the best. The suspected reason for the difference in the two results is thought to be because their method involved single atoms as features, whereas this method was dealing with entire functional groups. The smoothness of the gaussian distribution is probably a better estimator in that (especially with something like a phenyl ring). The optimized parameters for the method were found to be $C \approx 10$ and $\gamma \approx 0.05$.

@@

\begin{table}[H]
  \centering
  \caption{LUMO Results}
  \begin{tabular}{llr}
            Feature Vector     & Method       & MAE (eV)                \\
    \hline\hline
    \multirow{7}{*}{Naive}     & Mean Value   & 0.4475 $\pm$ 0.037 \\
                               & Linear       & 0.1900 $\pm$ 0.028 \\
                               & Linear Ridge & 0.1862 $\pm$ 0.025 \\
                               & Tree         & 0.1529 $\pm$ 0.007 \\
                               & k-NN         & 0.2351 $\pm$ 0.019 \\
                               & SVM Gauss    & \textbf{0.1055 $\pm$ 0.010} \\
                               & SVM Laplace  & 0.1454 $\pm$ 0.014 \\
    \hline
    \multirow{7}{*}{Decay}     & Mean Value   & 0.4475 $\pm$ 0.037 \\
                               & Linear       & 0.1816 $\pm$ 0.026 \\
                               & Linear Ridge & 0.1801 $\pm$ 0.026 \\
                               & Tree         & 0.1510 $\pm$ 0.024 \\
                               & k-NN         & 0.2323 $\pm$ 0.017 \\
                               & SVM Gauss    & \textbf{0.1022 $\pm$ 0.015} \\
                               & SVM Laplace  & 0.1317 $\pm$ 0.012 \\
    \hline
    \multirow{7}{*}{Decay with Length Corrections} & Mean Value   & 0.4475 $\pm$ 0.037 \\
                               & Linear       & 0.1847 $\pm$ 0.027 \\
                               & Linear Ridge & 0.1828 $\pm$ 0.027 \\
                               & Tree         & 0.1540 $\pm$ 0.023 \\
                               & k-NN         & 0.2348 $\pm$ 0.014 \\
                               & SVM Gauss    & \textbf{0.1029 $\pm$ 0.012} \\
                               & SVM Laplace  & 0.1331 $\pm$ 0.012 \\
    \hline
    \multirow{7}{*}{Decay with Predictions} & Mean Value   & 0.4475 $\pm$ 0.037 \\
                               & Linear       & 0.1233 $\pm$ 0.012 \\
                               & Linear Ridge & 0.0877 $\pm$ 0.011 \\
                               & Tree         & 0.0863 $\pm$ 0.010 \\
                               & k-NN         & 0.1699 $\pm$ 0.017 \\
                               & SVM Gauss    & \textbf{0.0792 $\pm$ 0.009} \\
                               & SVM Laplace  & 0.0922 $\pm$ 0.009 \\
    \hline\hline
  \end{tabular}
  \label{tab:lumoresults}
\end{table}
